Combining checkpointing and data compression\\ for large scale seismic inversion

### 2018-10-05 paper/paper.tex
Update figure and add attribution

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{images/survey-ship-diagram.png}
\end{center}
\caption{Illustration of an offshore seismic survey that collects the input data for seismic inversion}
\label{fig:offshore_survey}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{images/errors.pdf}
\end{center}
\caption{Cross-section of the field that shows errors introduced
  during compression and decompression using the fixed-tolerance
  mode. It is interesting to note that the errors are more or less
  evenly distributed across the domain with only slight variations
  corresponding to the wave amplitude (from the field plot in figure
  \ref{uncompressed}. A small block-like structure characteristic of
  ZFP can be seen.}
\label{fig:decompressed_error}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.75\linewidth]{images/survey-ship-diagram.jpg}
\end{center}
\caption{Illustration of an offshore seismic survey that collects the
  input data for seismic inversion. Source: The Open University \cite{surveyship}}
\label{fig:offshore_survey}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{images/errors.pdf}
\end{center}
\caption{Cross-section of the field that shows errors introduced
  during compression and decompression using the fixed-tolerance
  mode. It is interesting to note that the errors are more or less
  evenly distributed across the domain with only slight variations
  corresponding to the wave amplitude (from the field plot in figure
  \ref{fig:uncompressed}. A small block-like structure characteristic of
  ZFP can be seen.}
\label{fig:decompressed_error}
\end{figure}
